\documentclass[letterpaper]{article}
\usepackage[margin=0.5in,top=0.35in]{geometry}
\usepackage{titlesec}
\usepackage{changepage}
\usepackage{fontspec}
\usepackage{enumitem}

\setmainfont{Calibri}
\newcommand{\setfontsize}{\fontsize{11.5}{16}\selectfont}

% Disable page numbers
\pagenumbering{gobble}

% Don't number sections
\setcounter{secnumdepth}{0}
% Make section font size smaller and bolded
\titleformat*{\section}{\large\bfseries}
% Reduce the vertical space after sections
\titlespacing\section{2pt}{16pt}{3pt}

% Use hypens in lists instead of bullets
\def\labelitemi{-}
% Removing spacing in and around lists
\setlist{nolistsep}

% Macro for making section breaks
\newcommand{\sectionrule}[1] {
  \noindent\rule{\textwidth}{.1mm}
  \vspace{-11mm}
  \section{#1}
}

% Macro for indenting sections
\newenvironment{indentsection}
  {\begin{adjustwidth}{10mm}{0pt}}
  {\end{adjustwidth}}

% Macro for job headers
\newcommand{\job}[5] {
  \noindent\textbf{#1 \hfill #2}\\
  \textbf{#3 \hfill #4 - #5}

  \vspace{1mm}
}


% ---------------------------------------------------------------------------------------------------


\begin{document}
  \setfontsize

  \noindent{\Huge Shane Tully}
  \vspace{2mm}\\
  \noindent{\Large shane@shanetully.com \textbar\hspace{.5mm} shanetully.com}

  % -------------------------------------------------------------------------------------------------
  \sectionrule{Experience}

  \begin{indentsection}
    \job{Karat, Inc.}{Seattle, Washington}{Software Engineer}{January 2014}{Present}
    \begin{itemize}
      \item Built core product and supporting infrastructure with Ruby on Rails.
      \item Scaled interviewing capacity by automating interview scheduling, recording, and post-processing.
      \item Formulated structured scoring framework for assessing interviews of software engineering candidates.
      \item Deployed and managed company infrastructure on AWS and multiple production Linux servers.
    \end{itemize}

    \vspace{3mm}

    \job{Mozilla Corporation}{San Francisco, California}{Software Engineering Intern}{May 2013}{August 2013}
    \begin{itemize}
      \item Implemented contacts WebAPI in Firefox for Android.
      \item Created library for the Gecko engine to be used in third-party Android applications.
      \item Fixed various bugs in Firefox for Android.
    \end{itemize}

    \vspace{3mm}

    \job{Pennsylvania State University Chemistry Department}{University Park, Pennsylvania}{Web Developer}{June 2011}{December 2013}
    \begin{itemize}
      \item Developed online course and learning platform for university chemistry courses with Drupal and PHP.
      \item Built web-based interactive atomic orbital visualizations with JavaScript and Java.
      \item Managed Git server for team developers.
    \end{itemize}
  \end{indentsection}

  % -------------------------------------------------------------------------------------------------
  \sectionrule{Education}

  \begin{indentsection}
    \textbf{Bachelor of Science, Computer Science} \hfill December 2013\\
    Pennsylvania State University, University Park, PA \hfill Cumulative GPA: 3.23/4.00
  \end{indentsection}

  % -------------------------------------------------------------------------------------------------
  \sectionrule{Activities \& Projects}

  \begin{indentsection}
    \begin{itemize}
      \item Free and open source software contributor: https://github.com/shanet.
      \item Seven years Linux and server administration experience.
      \item Developed rocket telemetry system with embedded C++ on ARM architecture, Android, QT, and Ncurses control clients, and corresponding test suite.
      \item Volunteer as instructor for Girls Who Code teaching computer science fundamentals to middle school and high school girls in Bothell, WA.
      \item Manage Seattle GNU/Linux Conference's technical infrastructure for organizing conference data with OSEM in 2016.
      \item Developed AES encrypted, cross-platform chat application with Python, QT, and OpenSSL.
      \item Volunteered as webmaster and officer for the Penn State ACM student chapter, 2011 - 2013.
      \item Wrote API and server for networked, autonomous robot utilizing an iRobot Create and Microsoft Kinect.
      \item Built encrypted server and client for controlling ALSA on Linux desktops with C++, OpenSSL, and Android.
    \end{itemize}
  \end{indentsection}

  % -------------------------------------------------------------------------------------------------
  \sectionrule{Certifications}

  \begin{indentsection}
    \begin{itemize}
      \item FAA certified private pilot.
      \item FCC licensed amateur radio operator.
      \item NAR certified level 1 high power rocketry.
    \end{itemize}
  \end{indentsection}

\end{document}
